---
title: "hw03"
author: "Xiangyu Liu"
date: "2017-10-7"
output:
  md_document:
    variant: markdown_github
  html_document: null
---
##1. Functions in the R Base Package
```{r}
content <- mget(ls("package:base"), inherits = TRUE)
base_functions <- Filter(is.function, content)
library(purrr)
library(dplyr)
##a) Longest name
names <- map(names(base_functions), ~ .)  
length<- map(names,~nchar(.))%>% as.integer()
longest_name <- names[length==max(length)]
longest_name
```
The funtion 'getDLLRegisteredRoutines.character' has the longest name. 

```{r}
##b) Number of arguments
narg <- map(base_functions,~formals(.)) %>% lengths
top10=narg[order(narg,decreasing=TRUE)[1:10]]
list=list(name=names(top10),length=top10)
tbl_df(list)
```

```{r}
##c) No arguments
map(base_functions,~formals(.))[narg==0] %>% names %>% length
```

226 base functions have no arguments. They are primitive functions. The advantage of primitive functions is the potential efficiency of argument passing.

##2. Infant Mortality and GPD per Capita
```{r}
##a) Highest and lowest infant mortality rates in 2015
library(WDI)


data <- WDI(indicator=c("NY.GDP.PCAP.PP.KD","SP.DYN.IMRT.IN"), start=1960, end=2016, extra=TRUE) %>% rename(gdpcap= NY.GDP.PCAP.PP.KD, infmort=SP.DYN.IMRT.IN) %>% filter(!region=='Aggregates') ##keep only entries for countries


list <- filter(data, year =='2015')
list <- list[with(list,order(-infmort)),] %>% filter(!is.na(infmort))

selected_countries <- rbind(head(list,5),tail(list,5))
selected_countries <- selected_countries[,c(2,4,5)]
selected_countries
```
```{r}
##b) Overall regression
library(ggplot2)
lm(formula = infmort ~ gdpcap, data = data)
ggplot(data,aes(gdpcap,infmort)) + geom_point()+geom_smooth(na.rm=TRUE)
```
The infant mortality is inversely proportional to GDP per capita.#####
```{r}
##c) Regression by region
regiondata <- data %>% 
  filter(!is.na(region)) %>% 
  filter(!is.na(infmort))%>% 
  filter(!is.na(gdpcap)) %>%
  filter(region !='Aggregates')%>%
  select(infmort,gdpcap,region)

regionlist <- split(regiondata, regiondata$region)

coefs_region <- regionlist[2:8]%>%
  map(~ lm(infmort ~ gdpcap, data = .))%>%
  map(~ coef(.)) %>%
  map_dbl("gdpcap") %>%
  sort%>%
  as.data.frame()

coefs_region
```


```{r}
##d) Regression by country
countrydata <- data %>% 
  select(infmort,gdpcap,country)%>% 
  filter(!is.na(country)) %>% 
  filter(!is.na(infmort))%>% 
  filter(!is.na(gdpcap))

countrylist <- split(countrydata, countrydata$country)

coefs_country <- countrydata %>% 
  split(countrydata$country) %>%
  map(~ lm(infmort ~ gdpcap, data = .))%>%
  map(~ coef(.)) %>%
  map_dbl("gdpcap") %>%
  sort%>%
  as.data.frame()

count(coefs_country,coefs_country>0)

18/184
```
The percentage is 18/184.

```{r}
walk(coefs_country, hist)%>%
  map(summary)
head(coefs_country,1)
tail(coefs_country,1)
```
The country with the smallest coefficient is Guinea. Its  coefficient is -0.3521231. The country with the biggest coefficient is Madagascar. Its coefficient is 0.1300038. Because the overall regression estimated coefficient is -0.001005 . Therefore, Guinea cases are most at odds with the overall regression estimated in part(b).
```{r}
##e) Added squared term
rsquared_without_added<- countrydata %>% 
  split(countrydata$country) %>%
  map(~ lm(infmort ~ gdpcap, data = .)) %>%
  map(summary) %>%
  map_dbl("adj.r.squared")

countrydata$gdpcap2 <- countrydata$gdpcap * countrydata$gdpcap

rsquared_with_added<- countrydata %>% 
  split(countrydata$country) %>%
  map(~ lm(infmort ~ gdpcap+gdpcap2, data = .)) %>%
  map(summary) %>%
  map_dbl('adj.r.squared')

summary(rsquared_with_added)
summary(rsquared_without_added)
```
The average of adjusted R-squared with squared term is 0.74059. The average of adjusted R-squared without squared term is 0.66792. Because the average of adjusted R-squared with squared term is higher. So I recommend to keep the squared term.
